Finding Optimal Sequences for Area Aggregation --\protect\\ \Astar vs. Integer Linear Programming

### 2018-07-27 area_agg_seq_tsas.tex
submitted version to TSAS

\documentclass[acmlarge,review,natbib=false]{acmart}
\input{area_agg_seq_tsas_setting}

@@

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
Given two maps of the same region at two different scales,
a relevant problem is to compute maps for any intermediate scale.
We approach this problem for land-cover maps.
Given two land-cover maps at different scales, 
we want to find a sequence of small incremental
% To help map users not to lose context during zooming,
% we try to provide maps that change as continuous as possible.
% Since maps at some different scales often exist, 
% a relevant problem is to find maps at any intermediate scales.
% Given two land-cover maps of different scales, 
% we wish to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of polygons on the larger-scale map.

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
For solving such a problem optimally, standard approaches
are the \Astar algorithm or integer linear programming.
We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return nonoptimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal solutions for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

\keywords{Continuous map generalization, Land cover, 
	 Type chang, Compactness, Graph, Optimization, Exponential}

@@

We show how to compute an aggregation sequence for one region. 
For a goal map with many regions, 
after having found a sequence for each of them
we ``interleaf'' these aggregation sequences
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
merge sort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_Preliminaries}
	\caption{Integrating two aggregation sequences 
		of different regions: 
		the resulting sequence contains the given sequences 
		as subsequences and 
		always takes the subdivision with smallest patch next.
		The gray arrows show the integration of the two regions.
	}
	\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_Preliminaries}
	\caption{The subdivision graph~$G$. 
		The nodes of the graph are the subdivisions. 
		There is an arc	from subdivision~\Pnode 
		to subdivision~${P}_{t+1,j}$ 
		if ${P}_{t+1,j}$ is the result of 
		aggregating a smallest area~$p$ of~\Pnode with a 
		neighbor of~$p$.}
	\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

It is difficult to define exactly what reasonable means 
because users may have different preferences.
Four preferences are discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
They are aggregating a small land-cover area into one 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one is based on semantics and 
the other is based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, aggregating 
an area with type \emph{swamp} into an area with type \emph{wet 
	ground} rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by human being 
if it is more compact.
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness:
we consider a subdivision~\Pnode as more compact than
another subdivision~$P_{t,i'}$ if the total length of the interior boundaries of~\Pnode is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
see, for example, \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a reasonable replacement
when compactness is considered in an ILP
(e.g., \citealp{Minas2016,Wright1983}).
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is the centroid
that minimizes the sum.
The sum of the distances can also be computed linearly.
We use the length of interior boundaries 
instead of the distance because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_CostFunctions}
	\caption{An aggregation step, 
		where patch~$u$, the dark patch at the top,
		is aggregated into patch~$v$.
		Figures~(c) and~(d) respectively show the number of 
		edges and the lengths of the interior polylines after 
		the aggregation.}
	\label{fig:AreaAgg_FirstStep}	
\end{figure}

@@

\section{A Greedy Algorithm}
\label{sec:AreaAgg_Greedy}
At any time~$t$,
our greedy algorithm aggregates the smallest patch
with one of its neighbors.
Suppose that patch~$u$ is the smallest patch,
and patch~$v$ is one of~$u$'s neighbors.
We aggregate~$u$ into~$v$ 
if the type distances fulfill that
$d(T(u), T_\mathrm{goal}) \ge d(T(v), T_\mathrm{goal})$;
otherwise, we aggregate~$v$ into~$u$.
Recall that when we aggregate a patch into another patch,
the union takes the type of the latter.
We compute the costs of aggregating the smallest patch 
with each of the neighbors, 
and select the aggregation that costs least.
In other words, the smallest patch is aggregated with 
its most \emph{compatible} neighbor.
This idea is the same as that of \textcite{vanOosterom2005},
except we have a different definition for the compatible.
In accordance 
with our two combinatorial costs in 
\sect\ref{sec:AreaAgg_Combining},
we define two cost functions.
Suppose that we are at the step of 
aggregating from subdivision $P_{s,i}$ to subdivision 
$P_{s+1,j}$.
The first cost function is 
\begin{equation}
\label{eq:f_1}
f_1(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{comp}}(P_{s+1,j}). \nonumber
\end{equation}
The second cost function is
\begin{equation}
\label{eq:f_2}
f_2(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{lgth}}(P_{s+1,j}). \nonumber
\end{equation}

@@

%\mypar[inline]{Motivate \Astar by comparison with Dijkstra.}

We try to find a shortest path,
from the start map to the goal map,
using \Astar \citep{Hart1968}.  
As the graph~$G$---our search space---can be of exponential size 
(see \sect\ref{sec:AreaAgg_Preliminaries}), 
we avoid computing the whole graph explicitly.
To save time and memory, 
we generate a subdivision \Pnode only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivisions~$\Pstart$ to~$\Pgoal$.  
For subdivision \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal.  
\Astar can be seen as a refinement of Dijkstra's algorithm
where nodes are explored earlier 
if they are estimated to be closer to the goal.

More formally, we define $g(\Pnode)$ to be 
the exact cost of a shortest path from~\Pstart to~\Pnode, 
and we define $h(\Pnode)$ to be the estimated cost 
to get from \Pnode to~\Pgoal. 
Then the (estimated) total cost at node~\Pnode is
\begin{equation}
\label{eq:CostTotal}
F(\Pnode)=g(\Pnode)+h(\Pnode).
\end{equation}
We use either~$g_1$ (\eq\ref{eq:g_1}) 
or~$g_2$ (\eq\ref{eq:g_2})
for~$g(\Pnode)$.
If~$h(\Pnode)$ is always bounded from above 
by the exact cost of a shortest path from~\Pnode to~\Pgoal, 
\Astar is guaranteed to find a shortest path from~\Pstart 
to~\Pgoal, 
that is, an optimal aggregation sequence.  
Using the estimation~$F$ (\eq\ref{eq:CostTotal}), 
\Astar is able to reduce the search space.
The better the estimation part~$h$, 
the more \Astar can reduce the search space.
In the following, we show how we compute
estimated cost $h(\Pnode)$.

@@

At time $s$, there are $n-s+1$ patches.
There can be as few as $n-s$ interior boundaries.
In order to find a lower bound of the cost of length,
we keep only the necessary number, $n-s$, 
of shortest boundaries at each step
(see \fig\ref{fig:AreaAgg_h_length}).
Then we compute the estimated cost of length according to 
\eq\ref{eq:f_length}.

@@

Now we change our problem a bit.
We assume that we want to sell coffee in bottles,
where each bottle contains exactly~$1\,$kg of coffee 
with intensity either~$40\%$ or~$20\%$.
Our question becomes how many bottles of each kind of coffee
we should sell in order to maximize the profit.
If we sell the two kinds of coffee 
respectively~$x'$ and~$y'$ bottles,
then our problem becomes:
\begin{alignat*}{3}
&&\text{maximize} 	\quad	&& 5x'+4y' 		&			\\
&&\text{subject to} \quad	&& 0.4x'+0.2y'	&\le 3.5, 	\\
&&					\quad	&& 0.6x'+0.8y' 	&\le 10, 	\\
&&					\quad	&& x', y' 		&\ge 0, 	\\
&&\text{and} 		\quad	&& x', y'		&\in \mathbb{Z}.
\end{alignat*}
For this problem, only the pairs of~$(x,y)$ 
represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
are feasible solutions
(point~$A$ is no longer an optimal solution in this case).
In order to maximize our profit,
we should move the dashed line to the upper right 
as much as possible
and at the same time make sure that 
it hits at least one of the gray dots.
To solve such a problem is known as
\emph{integer linear programming},
which is NP-complete.
Despite the fact, there are
mathematical solvers yielding optimal solutions
for some NP-complete problems in reasonable time
\parencite{Haunert2017Label}.
Also, by using these solvers we profit 
from every improvement, by their producers,
for the same class of problems
\parencite{Haunert2017Label}.
The general form of an \emph{integer linear program} (ILP) is
\begin{alignat*}{3}
&&\text{maximize} 	\quad&& \bm{C}^\mathrm{T}\bm{X}	&		\\
&&\text{subject to} \quad&& \bm{EX}			&\le \bm{H}, 	\\
&&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
\end{alignat*}
where vector~$\bm{X}$ represents integer variables, 
vector~$\bm{C} \in \mathbb{R}^I$, 
vector~$\bm{H} \in \mathbb{R}^J$,
and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
Furthermore, if we require that
$$
\bm{X} 	\in \{0,1\}^I,
$$
then we have only binary variables for an ILP.
Binary variables are important 
because they occur regularly in optimizations
\parencite[section~9.2]{bradley1977applied}.
Also, an ILP with general (bounded) integer variables 
can always be translated to an ILP with binary variables
\parencite[section~2.3]{Williams2009Integer}.
To find optimal sequences for area aggregation, 
we are going to use binary variables in our ILP.

@@

Our problem is to decide centers for polygons to be assigned.
Each question of type 
``Is polygon~$p$ assigned to center~$r$?''
can be answered with ``yes'' or ``no''.
Hence, we use binary ($0$--$1$) variables.
We need five sets of variables
in order to formulate our pathfinding problem as an ILP.
%
The first set of variables is used to tell the program 
our rules for area aggregation.
\begin{figure*}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_ILP}
	\caption{Some examples of variables~$x$,~$y$, and~$z$ for our ILP. 
		The arrows in the figures show the aggregation steps and
		the dotted lines represent the removed boundaries by the aggregation steps.
	}
	\label{fig:AreaAgg_Variables}
\end{figure*}
We introduce the variable 
\begin{flalign*}
&\myquad[4]
\embrd[V]{x_{t,p,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T, \forall p,r \in P&
\end{flalign*}
with the intended meaning~$x_{t,p,r}=1$ if and only if 
polygon $p$ is assigned to polygon $r$ at time $t$. 
If a polygon is a center at time~$t$, 
then the polygon must be assigned to itself, 
that is, $x_{t,r,r}=1$
(see \fig\ref{fig:AreaAgg_Variables} for some examples).

Our second set of variables is used to compute the
cost of type change.  We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{y_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1\}, \forall p,o,r \in P&
\end{flalign*}
with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
polygon~$p$ is assigned to center $o\in P$ at time~$t-1$ 
and to center~$r$ at time~$t$.
Specifically, $y_{t,p,o,o}=1$ means that
polygon~$p$ is assigned to the same center 
at times~$t-1$ and~$t$ 
(see \fig\ref{fig:AreaAgg_Variables}).

We need a third set of variables 
for computing the cost of length.
We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{z_{t,p,q,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1,n\}, \forall p,q,r \in P&
\end{flalign*}
with the intended meaning~$z_{t,p,q,r}=1$ 
if and only if at time~$t$
polygons~$p$ and~$q$ are both in patch~$r$.
In this case, their common boundary should be removed
(see \fig\ref{fig:AreaAgg_Variables}).
When variable~$z_{t,p,q,r}=1$ and~$p=q$,
we define the length of their common boundary to be~$0$ 
because we shall not remove any.
Note that time $t\in T\setminus \{1,n\}$.
We do not need~$z_{t,p,q,r}$ for time~$t=1$ 
because at the time
there are no two polygons in the same patch.
Namely, it always holds that~$z_{1,p,q,r}=0$, 
which does not help in our ILP.
We do not need~$z_{t,p,q,r}$ for time~$t=n$
because in this case
all the polygons are in the same patch.
The situation that~$z_{n,p,q,r}=1$ always holds
does not help in our ILP, either.

We use a fourth set of variables
to guarantee contiguity of each patch. 
In other words, we aggregate two patches 
only when they are neighbors (adjacent).
We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{c_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{n-1,n\}, 
\forall p,o,r \in P \text{~with}~o\ne r,&
\end{flalign*}
with the intended meaning~$c_{t,p,o,r}=1$ 
if and only if at time~$t$
polygon~$p$ is assigned to center~$o$ 
and~$p$ has a neighbor assigned to center~$r$
(see for example \fig\ref{fig:AreaAgg_Variables_Neighbor}).
We do not need a variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
because then there are only two patches left 
and they must be neighbors.

Our last set of variables is needed to 
enforce that
every aggregation step involves a smallest patch. 
We define
\begin{flalign*}
&\myquad[4]
\embrd[V]{w_{t,o}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus\{n\}, \forall o \in P&
\end{flalign*}
with $w_{t,o}=1$ meaning 
that patch~$o$ is a smallest patch at time~$t$.

@@

Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
or~$p$ is not assigned to~$r$ at time $t$ ($x_{t,p,o}=0$),
then $y_{t,p,o,r}=0$.
This is expressed by
\begin{flalign}
\label{eq:CstrY2}
&\eqquad
\begin{array}{@{}l}
\embrd{y_{t,p,o,r}} \le \\
\embrd{y_{t,p,o,r}} \le 
\end{array}
\embld{\hspace{0.5pt}
	\begin{array}{@{}l}
	x_{t-1,p,o} \\
	x_{t,p,r}
	\end{array}
	\bigg\} 
}
\inquad \hspace{0.5pt}
\forall t\in T\setminus \{1\}, 
\forall	p,o,r \in P.&	
\end{flalign}

>>>>

\documentclass[acmsmall,natbib=false]{acmart}
\input{area_agg_seq_tsas_setting}

@@

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
We approach this problem for land-cover maps.
%Given two maps of the same region at two different scales,
%a relevant problem is to compute maps for any intermediate scale.
Given two land-cover maps at two different scales, 
we want to find a sequence of small incremental
% To help map users not to lose context during zooming,
% we try to provide maps that change as continuous as possible.
% Since maps at some different scales often exist, 
% a relevant problem is to find maps at any intermediate scales.
% Given two land-cover maps of different scales, 
% we wish to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of polygons on the larger-scale map.

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
%We compared the \Astar algorithm and 
%integer linear programming in solving this problem.
For solving such a problem, standard approaches
are the \Astar algorithm or integer linear programming.
%We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return nonoptimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

\keywords{Continuous map generalization, Land cover, 
	 Type change, Compactness, Shortest path
%	 , Optimization, Exponential
	 }

@@

We show how to compute an aggregation sequence for one region. 
For a goal map with many regions, 
after having found a sequence for each of them
we ``interleave'' these aggregation sequences
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
merge sort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
\centering
\includegraphics[page=1]{AreaAgg_Preliminaries}
\caption{Integrating two aggregation sequences 
	of different regions: 
	the resulting sequence contains the given sequences 
	as subsequences and 
	always takes the subdivision with smallest patch next.
	The gray arrows show the integration of the two regions.
}
\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_Preliminaries}
\caption{The subdivision graph~$G$. 
	The nodes of the graph are the subdivisions. 
	There is an arc	from subdivision~\Pnode 
	to subdivision~${P}_{t+1,j}$ 
	if~${P}_{t+1,j}$ is the result of 
	aggregating a smallest area~$p$ of~\Pnode with a 
	neighbor of~$p$.}
\label{fig:AreaAgg_SubdivisionName}
\end{figure}

@@

It is difficult to define exactly what reasonable means 
because users may have different preferences.
Four preferences are discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
They are aggregating a small land-cover area into one 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one is based on semantics and 
the other is based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by human being 
if it is more compact (less clutter).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness:
we consider a subdivision~\Pnode as more compact than
another subdivision~$P_{t,i'}$ if the total length of the interior boundaries of~\Pnode is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
see, for example, \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a reasonable replacement
when compactness is considered in an ILP
(e.g., \citealp{Minas2016,Wright1983}).
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is the centroid
that minimizes the sum.
The sum of the distances can also be computed linearly.
We use the length of interior boundaries 
instead of the distance because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

\begin{figure}[tb]
\centering
\includegraphics[page=2]{AreaAgg_CostFunctions}
\caption{An aggregation step, 
	where patch~$u$, the dark patch at the top,
	is aggregated into patch~$v$.
	\figs(c) and~(d) respectively show the number of 
	edges and the lengths of the interior polylines after 
	the aggregation.}
\label{fig:AreaAgg_FirstStep}	
\end{figure}

@@

\section{A Greedy Algorithm}
\label{sec:AreaAgg_Greedy}
At any time~$t$,
our greedy algorithm aggregates the smallest patch
with one of its neighbors.
Suppose that patch~$u$ is the smallest patch,
and patch~$v$ is one of~$u$'s neighbors.
We aggregate~$u$ into~$v$ 
if the type distances fulfill that
$d\left(T(u), T_\mathrm{goal}\right) 
\ge d\left(T(v), T_\mathrm{goal}\right)$;
otherwise, we aggregate~$v$ into~$u$.
Recall that when we aggregate a patch into another patch,
the union takes the type of the latter.
We compute the costs of aggregating the smallest patch 
with each of the neighbors, 
and select the aggregation that costs least.
In other words, the smallest patch is aggregated with 
its most \emph{compatible} neighbor.
This idea is the same as that of \textcite{vanOosterom2005},
except that we have a different definition 
for the compatibility.
In accordance with our two combinatorial costs in 
\sect\ref{sec:AreaAgg_Combining},
we define two cost functions.
Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$.
The first cost function is 
\begin{equation}
\label{eq:f_1}
f_1(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{comp}}(P_{s+1,j}). \nonumber
\end{equation}
The second cost function is
\begin{equation}
\label{eq:f_2}
f_2(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{lgth}}(P_{s+1,j}). \nonumber
\end{equation}

@@

We try to find a shortest path,
from the start map to the goal map,
using \Astar \parencite{Hart1968,PatelAStar}.  
As the graph~$G$---our search space---can 
be of exponential size 
(see \sect\ref{sec:AreaAgg_Preliminaries}), 
we avoid computing the whole graph explicitly.
To save time and memory, 
we generate a subdivision \Pnode only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivisions~$\Pstart$ to~$\Pgoal$.  
For subdivision \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal.  
\Astar can be seen as a refinement of Dijkstra's algorithm
where nodes are explored earlier 
if they are estimated to be closer to the goal.

More formally, we define~$g(\Pnode)$ to be 
the exact cost of a shortest path from~\Pstart to~\Pnode, 
and we define~$h(\Pnode)$ to be the estimated cost 
to get from \Pnode to~\Pgoal. 
Then the (estimated) total cost at node~\Pnode is
\begin{equation}
\label{eq:CostTotal}
F(\Pnode)=g(\Pnode)+h(\Pnode).
\end{equation}
We use either~$g_1$ (\eq\ref{eq:g_1}) 
or~$g_2$ (\eq\ref{eq:g_2})
for~$g(\Pnode)$.
If~$h(\Pnode)$ is always bounded from above 
by the exact cost of a shortest path from~\Pnode to~\Pgoal, 
\Astar is guaranteed to find a shortest path from~\Pstart 
to~\Pgoal, 
that is, an optimal aggregation sequence.  
Using the estimation~$F$ (\eq\ref{eq:CostTotal}), 
\Astar is able to reduce the search space.
The better the estimation part~$h$, 
the more \Astar can reduce the search space.
In the following, we show how we compute
estimated cost $h(\Pnode)$.

@@

At time $s$, there are $n-s+1$ patches.
There can be as few as $n-s$ interior boundaries.
In order to find a lower bound for the cost of length,
we keep only the necessary number, $n-s$, 
of shortest boundaries at each step
(see \fig\ref{fig:AreaAgg_h_length}).
Then we compute the estimated cost of length according to 
\eq\ref{eq:f_length}.

@@

Now we change our problem a bit.
We assume that we want to sell coffee in bottles,
where each bottle contains exactly~$1\,$kg of coffee 
with intensity either~$40\%$ or~$20\%$.
Our question becomes how many bottles of each kind of coffee
we should sell in order to maximize the profit.
If we sell the two kinds of coffee 
respectively~$x'$ and~$y'$ bottles,
then our problem becomes:
\begin{alignat*}{3}
&&\text{maximize} 	\quad	&& 5x'+4y' 		&			\\
&&\text{subject to} \quad	&& 0.4x'+0.2y'	&\le 3.5, 	\\
&&					\quad	&& 0.6x'+0.8y' 	&\le 10, 	\\
&&					\quad	&& x', y' 		&\ge 0, 	\\
&&\text{and} 		\quad	&& x', y'		&\in \mathbb{Z}.
\end{alignat*}
For this problem, only the pairs of~$(x,y)$ 
represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
are feasible solutions
(point~$A$ is no longer an optimal solution in this case).
In order to maximize our profit,
we should move the dashed line to the upper right 
as much as possible
and at the same time make sure that 
it hits at least one of the gray dots.
To solve such a problem is known as
\emph{integer linear programming},
which is NP-complete.
Despite the fact, there are
mathematical solvers yielding optimal solutions
for some NP-complete problems in reasonable time
\parencite{Haunert2017Label}.
Also, by using these solvers we profit 
from every improvement, by their producers,
for the same class of problems
\parencite{Haunert2017Label}.
The general form of an \emph{integer linear program} (ILP) is
\begin{alignat*}{3}
&&\text{maximize} 	\quad&& \bm{C}^\mathrm{T}\bm{X}	&		\\
&&\text{subject to} \quad&& \bm{EX}			&\le \bm{H}, 	\\
&&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
\end{alignat*}
where vector~$\bm{X}$ represents integer variables, 
vector~$\bm{C} \in \mathbb{R}^I$, 
vector~$\bm{H} \in \mathbb{R}^J$,
and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
Furthermore, if we require that
$$
\bm{X} 	\in \{0,1\}^I,
$$
then we have only binary variables for an ILP.
Binary variables are important 
because they occur regularly in optimizations
\parencite[\sect9.2]{bradley1977applied}.
Also, an ILP with general (bounded) integer variables 
can always be translated to an ILP with binary variables
\parencite[\sect2.3]{Williams2009Integer}.
To find optimal sequences for area aggregation, 
we are going to use binary variables in our ILP.

@@

Our problem is to decide centers for polygons to be assigned.
Each question of type 
``Is polygon~$p$ assigned to center~$r$?''
can be answered with ``yes'' or ``no''.
Hence, we use binary ($0$--$1$) variables.
We need five sets of variables
in order to formulate our pathfinding problem as an ILP.
%
The first set of variables is used to tell the program 
our rules for area aggregation.
\begin{figure*}[tb]
\centering
\includegraphics[page=1]{AreaAgg_ILP}
\caption{Some examples of the five sets of variables 
	for our ILP, $x$, $y$, $z$, $c$, and~$w$.
	The arrows in the drawings 
	show the aggregation steps and
	the dotted lines represent 
	the removed boundaries by the aggregation steps.
	There are some blank spaces because there is no corresponding variable at the specific times.
}
\label{fig:AreaAgg_Variables}
\end{figure*}
We introduce the variable 
\begin{flalign*}
&\myquad[6]
\embrd[V]{x_{t,p,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T, \forall p,r \in P&
\end{flalign*}
with the intended meaning~$x_{t,p,r}=1$ if and only if 
polygon $p$ is assigned to polygon $r$ at time $t$. 
If a polygon is a center at time~$t$, 
then the polygon must be assigned to itself, 
that is, $x_{t,r,r}=1$
(see \fig\ref{fig:AreaAgg_Variables} for some examples).

Our second set of variables is used to compute the
cost of type change.  We introduce
\begin{flalign*}
&\myquad[6]
\embrd[V]{y_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1\}, \forall p,o,r \in P&
\end{flalign*}
with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
polygon~$p$ is assigned to center $o\in P$ at time~$t-1$ 
and to center~$r$ at time~$t$.
Specifically, $y_{t,p,o,o}=1$ means that
polygon~$p$ is assigned to the same center 
at times~$t-1$ and~$t$ 
(see \fig\ref{fig:AreaAgg_Variables}).

We need a third set of variables 
for computing the cost of length.
We introduce
\begin{flalign*}
&\myquad[6]
\embrd[V]{z_{t,p,q,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1,n\}, \forall p,q,r \in P&
\end{flalign*}
with the intended meaning~$z_{t,p,q,r}=1$ 
if and only if at time~$t$
polygons~$p$ and~$q$ are both in patch~$r$.
In this case, their common boundary should be removed
(see \fig\ref{fig:AreaAgg_Variables}).
When variable~$z_{t,p,q,r}=1$ and~$p=q$,
we define the length of their common boundary to be~$0$ 
because we shall not remove any.
Note that time $t\in T\setminus \{1,n\}$.
We do not need~$z_{t,p,q,r}$ for time~$t=1$ 
because at the time
there are no two polygons in the same patch.
Namely, it always holds that~$z_{1,p,q,r}=0$, 
which does not help in our ILP.
We do not need~$z_{t,p,q,r}$ for time~$t=n$
because in this case
all the polygons are in the same patch.
The situation that~$z_{n,p,q,r}=1$ always holds
does not help in our ILP, either.

We use a fourth set of variables
to guarantee contiguity of each patch. 
In other words, we aggregate two patches 
only when they are neighbors (adjacent).
We introduce
\begin{flalign*}
&\myquad[6]
\embrd[V]{c_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{n-1,n\}, 
\forall p,o,r \in P \text{~with}~o\ne r,&
\end{flalign*}
with the intended meaning~$c_{t,p,o,r}=1$ 
if and only if at time~$t$
polygon~$p$ is assigned to center~$o$ 
and~$p$ has a neighbor assigned to center~$r$
(see for example \figs\ref{fig:AreaAgg_Variables}
and~\ref{fig:AreaAgg_Variables_Neighbor}).
We do not need a variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
because then there are only two patches left 
and they must be neighbors.

Our last set of variables is needed to 
enforce that
every aggregation step involves a smallest patch. 
We define
\begin{flalign*}
&\myquad[6]
\embrd[V]{w_{t,o}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus\{n\}, \forall o \in P&
\end{flalign*}
with $w_{t,o}=1$ meaning 
that patch~$o$ is a smallest patch at time~$t$
(see for example \fig\ref{fig:AreaAgg_Variables}).

@@

Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
then $y_{t,p,o,r}=0$.
This is expressed by
\begin{flalign}
\label{eq:CstrY2}
&\eqquad
\begin{array}{@{}l}
\embrd{y_{t,p,o,r}} \le \\
\embrd{y_{t,p,o,r}} \le 
\end{array}
\embld{\hspace{0.5pt}
	\begin{array}{@{}l}
	x_{t-1,p,o} \\
	x_{t,p,r}
	\end{array}
	\bigg\} 
}
\inquad \hspace{0.5pt}
\forall t\in T\setminus \{1\}, 
\forall	p,o,r \in P.&	
\end{flalign}
